\begin{thebibliography}{9}
\addcontentsline{toc}{section}{References}

\bibitem{ipbook}
  R. Woods, R. Gonzalez \\
  \emph{Digital Image Processing.} \\
  3rd Edition, 2007

\bibitem{mooreslaw}
  R Schaller \\	
  \emph{Moore's law: past, present, and future.} \\
  1997

\bibitem{mooreslawdata}
  \emph{Moore's Law for Intel CPUs.} \\
  http://www.physics.udel.edu/~watson/scen103/intel.html [2014-09-04]

\bibitem{cudaexample}
  J. Sanders, E. Kandrot \\
  \emph{CUDA By Example.} \\
  1st Edition,  2010.

\bibitem{glredbook}
  OpenGL ARB, D. Shreiner, M. Woo, J. Neider, T. Davis \\
  \emph{OpenGL Programming Guide: The Official Guide to Learning OpenGL.} \\
  5th Edition, 2005.

\bibitem{glshadinglanguage}
  R. J. Rost\\
  \emph{OpenGL Shading Language.}\\
  2nd Edition, 2006.

\bibitem{cudapguide}
  NVIDIA \\
  \emph {CUDA C Progamming Guide.} \\
  http://docs.nvidia.com/cuda/cuda-c-programming-guide/ [2014-09-04]

\bibitem{opencl}
  Khronos OpenCL Working Group \\
  \emph{The OpenCL Specification.} \\
  Version 2.0, 2014.

\bibitem{cudaoptimize}
  NVIDIA \\
  \emph{CUDA C Best Practices Guide.} \\
  http://docs.nvidia.com/cuda/cuda-c-best-practices-guide [2014-09-04]

\bibitem{smartpointer}
  Gregory Colvin \\
  \emph{Exception Safe Smart Pointers.} \\
  C++ committee document 94-168/N0555, 1994.

\bibitem{designpatterns}
  E. Gamma, R. Helm, R. Johnson, J Vlissides \\
  \emph{Subject	Design patterns, software engineering, object-oriented programming.} \\
  1st Edition, 1994.

\bibitem{qt}
  Digia plc \\
  \emph {Qt Project.} \\
  http://qt-project.org/ [2014-09-04]

\bibitem{pyside}
  \emph {PySide, Python For Qt.} \\
  http://qt-project.org/wiki/PySide [2014-09-04]

\bibitem{boostpython}
  \emph {Boost Python.} \\
  www.boost.org/libs/python/doc/ [2014-09-04]

\bibitem{cimg}
  \emph{The CImg Library.} \\
  http://cimg.sourceforge.net/ [2014-09-04]

\bibitem{openexr}
  Industrial Light \& Magic \\
  \emph{OpenEXR.} \\
  http://www.openexr.com [2014-09-04]

\bibitem{exrdisplay}
  Industrial Light \& Magic \\
  \emph{Using exrdisplay.} \\
  http://www.openexr.com/using.html [2014-09-04]

\bibitem{cmake}
  KitWare \\
  \emph{CMake.} \\
  http://www.cmake.org/ [2014-09-04]

\bibitem{doxygen}
  \emph{Doxygen.} \\
  http://www.doxygen.org/ [2014-09-04]

\bibitem{boostcompute}
  Kyle Lutz \\
  \emph{Boost Compute.} \\
  http://kylelutz.github.io/compute/ [2014-09-04]

\bibitem{cudathrust}
  NVIDIA \\
  \emph{Thrust.} \\
  http://docs.nvidia.com/cuda/thrust/ [2014-09-04]


\end{thebibliography}
