\subsection{Limitations}

As discussed in the previous chapter, there are different categories in image processing. This thesis will focus on the case where an input image is used to produce an output image, mainly because it is hard to generalize things like feature extraction across all GPU environments. The framework is instead going to support algorithms where an arbitrary number of input images are going to produce an arbitrary number of output images. The number of input images and output images do not have to match. The framework needs to support multipass algorithms where multiple GPU programs are being called sequentially and where the output of one program can be the input of the following one. The framework is going support images with one to four channels of colors and where the data has either floating point precision or is of the unsigned byte type (often referred to as unsigned char).
\newline

The framework is going to support the following common GPU computing environments:

\begin{itemize}
\item{{\bf CUDA} - NVIDIA}
\item{{\bf OpenCL} - Khronos Group}
\item{{\bf GLSL} - OpenGL Shading Language}
\end{itemize}

CUDA and OpenCL are the two most common choices today in the world of general-purpose GPU computing. Before OpenCL and CUDA, people used programmable shaders in 3D graphics libraries such as OpenGL and DirectX to perform image processing on the GPU. Since DirectX and their HLSL shading language and Direct Compute environment only are supported on Microsoft Windows systems, they are not included in the framework of this thesis. The framework is meant to be flexible and cross-platform, supporting Unix, Mac OSX and Windows operating systems.
